### 2020-01-31 Common/chapters/paper_reproduction.tex
Johan and Julien: Tensorboard section first draft

\section{Training the neural network}
\subsection{Architecture}
The model architecture used in the paper is a modified version of the VGG network from the Oxford's Visual Geometry Group (VGG). This model was initially designed as part of the Large Scale Visual Recognition Challenge 2014 that used the ImageNet dataset of 14 millions images belonging to 1000 classes. The figure \ref{fig:paper_model} illustrates its structure and its corresponding implementation in Python with the PyTorch Framework.\\
It is first composed by three convolution-dropout-max-pooling blocks followed by three fully connected-dropout blocks. Each convolutional box (in blue) in the figure represents in reality three layers: the convolutional layer, the batch normalization layer and the exponential linear unit activation function. The same principle is used for the fully connected layer box (in orange) that is divided into a fully connected layer followed by the exponential linear unit. The last fully connected box (in purple) has the same structure except that the exponential linear unit is replaced by a softmax  function for classification.\\
In comparison to the original VGG, this model keeps the small filter size of 3x3 or 1x1,  also doubles the number of filters after each convolution-dropout-max-pooling block and has a stride of 1 for all convolutions. It differs from the traditional VGG in that it makes use of a smaller number of layer since the task is simpler than the original one, it uses exponential linear units instead of rectified linear units as activation functions and adds dropout and batch normalization layers.
\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/model_paper_manual.png}
\caption{Model architecture with the corresponding PyTorch code}
\label{fig:paper_model}
\end{figure}
\subsection{Criterion to save the best model}
\subsection{Tensorboard}
\label{paper_tensorboard}
\subsection{Script options}
\subsection{Experimental setup}
\subsection{Training verification}
\subsubsection{Gradient flow visualization}

>>>>

\section{Training the neural network}
\subsection{Architecture}
The model architecture used in the paper is a modified version of the VGG network from the Oxford's Visual Geometry Group (VGG). This model was initially designed as part of the Large Scale Visual Recognition Challenge 2014 that used the ImageNet dataset of 14 millions images belonging to 1000 classes. The figure \ref{fig:paper_model} illustrates its structure and its corresponding implementation in Python with the PyTorch Framework.\\
It is first composed by three convolution-dropout-max-pooling blocks followed by three fully connected-dropout blocks. Each convolutional box (in blue) in the figure represents in reality three layers: the convolutional layer, the batch normalization layer and the exponential linear unit activation function. The same principle is used for the fully connected layer box (in orange) that is divided into a fully connected layer followed by the exponential linear unit. The last fully connected box (in purple) has the same structure except that the exponential linear unit is replaced by a softmax  function for classification.\\
In comparison to the original VGG, this model keeps the small filter size of 3x3 or 1x1,  also doubles the number of filters after each convolution-dropout-max-pooling block and has a stride of 1 for all convolutions. It differs from the traditional VGG in that it makes use of a smaller number of layer since the task is simpler than the original one, it uses exponential linear units instead of rectified linear units as activation functions and adds dropout and batch normalization layers.
\begin{figure}[!h]
\centering
\includegraphics[width=1\textwidth, keepaspectratio=true]{./figures/model_paper_manual.png}
\caption{Model architecture with the corresponding PyTorch code}
\label{fig:paper_model}
\end{figure}
\subsection{Criterion to save the best model}
\subsection{Tensorboard}
During the experiment the following metrics are registered: loss, accuracy, precision, recall, F1-score, specificity and AUC. These metrics are computed separately on the training and on the validation sets at the end of each epoch. They are then stored across all epochs and plotted on the same figure thanks to Tensorboard at the end of the process. Subsequently, this is also the case for the metrics measured on the test set.\\
"Tensorboard provides the visualization and tooling needed for machine learning experimentation:
\begin{itemize}
\item Tracking and visualizing metrics.
\item Visualizing the model graph (ops and layers).
\item Viewing histograms of weights, biases, or other tensors as they change over time.
\item Projecting embeddings to a lower dimensional space.
\item Displaying images, text, and audio data"\cite{39}.
\end{itemize}
In this experiment, Tensorboard is mainly used to plot the Matplotlib figures of the model performance. In addition to this, written reports regarding which model was the best and the results it reached are also added on the dashboard.
\label{paper_tensorboard}
\subsection{Script options}
\subsection{Experimental setup}
\subsection{Training verification}
\subsubsection{Gradient flow visualization}
